### 2021-07-19 doc/thesis/chapters/system-design-process.tex
v-modell diagram

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Design Targeting FPGAs}
The research for this chapter is mainly based on \cite{GesslerRalf2014EES}.
%https://link-springer-com.fhooe.idm.oclc.org/content/pdf/10.1007%2F978-3-319-26408-0.pdf
%chapter 3

@@

%applies to general software development, but can directly be mapped to FPGA development.

%Abbildung 3.5 in
%https://link-springer-com.fhooe.idm.oclc.org/content/pdf/10.1007%2F978-3-8348-2080-8.pdf

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{High-Level Synthesis}
%\cplusplus\\
%SystemC (deprecated for synthesis by Xilinx)\\

A comprehensive list of HLS tools can be found in Section 3.3 of
%https://link-springer-com.fhooe.idm.oclc.org/content/pdf/10.1007%2F978-3-319-26408-0.pdf

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Implementation with Tool Support}
%https://link-springer-com.fhooe.idm.oclc.org/content/pdf/10.1007%2F978-3-8348-2080-8.pdf

%Matlab Simulink System Generator\\
%Matlab Simulink HDL Coder\\

@@

%direct, or 'manual' implementation\\
%VHDL/Verilog\\

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{System Design Targeting FPGAs}

A wide range of design approaches are available that are targeting FPGAs.
In this section, some selected approaches are described.
The research for this section is mainly based on \cite{GesslerRalf2014EES}.

@@

applies to general software development, but can directly be mapped to FPGA development.

\includepicture [1.0] [0] [H] {The V-Modell \cite[Abbildung 3.5]{GesslerRalf2014EES}.} {v_modell} {img/draw.io/v_modell}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{High-Level Synthesis}
\cplusplus\\
SystemC (deprecated for synthesis by Xilinx)\\

A comprehensive list of HLS tools can be found in Section 3.3 of \cite{2016FfSP}

HLS is described into more detail in section \ref{cha:HLS}.

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Implementation with Tool Support}
see \cite{GesslerRalf2014EES}\\

Matlab Simulink System Generator\\
Matlab Simulink HDL Coder\\

@@

direct, or 'manual' implementation\\
VHDL/Verilog\\
